Manuscript draft

### 2019-09-11 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

[**THIS PARAGRAPH NEEDS ATTENTION!**]. We show that fluxes are broadly consistent in their responses to climate drivers on the global scale (with the exception of some differences in MAT-MAP interactions; Fig. 4), with no major trends in C allocation among the variable pairs tested (Fig. 2; **Some SI table**). *This finding does not support some of the dominant current understanding, with significant implications for our understanding of FACF responses to climatic warming.* Of particular interest are the relationships between $GPP$ and respiration ($R_{auto}$, $R_{root}$) or net primary productivity ($NPP$, $ANPP$, $BNPP$). The dominant current understanding is that *respiration responds more strongly to temperature than does photosynthesis (**REFS(KAT)**)*, and that carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$) is lowest in the tropics (**REFS(KAT)**). The latter understanding is driven by observations of low $CUE$ in old-growth tropical forests relative to extratropical forests [@de_lucia_forest_2007; @anderson-teixeira_carbon_2016] (**REFS(KAT)**), but our analysis suggests that these low values may more appropriately be attributed to the fact that these forests are old than to their climate. Indeed, $CUE$ is known to decline with forest age ([@de_lucia_forest_2007];**REFS(NOBBY)**). Whereas autotrophic respiration responds more strongly to temperature than does photosynthesis on short time scales (**REFS(KAT)**), our findings indicate that annual C allocation to respiration is roughly independent of temperature.  [There is some indication that $GPP$ may have a somewhat steeper and less variable relationship to latitude and temperature than does $ANPP_{woody-stem}$ (Fig. 2; see also Larjavaara & Muller-Landau (2011)?), but standardized slopes are not signficnatly different (**??-BECKY**). (**Helene, maybe comment on Larjavaara & Muller-Landau (2011)?**). ] While our analysis indicates that climate shapes most FACFs in similar ways on the global scale, careful methodological standardization across a consistent set of mature forest sites could potentially reveal modest but potentially signficant trends in carbon allocation along global climatic gradients. 
[There is evidence that allocation between carbon fluxes does vary with factors such as stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], forest structure [@taylor_greater_2019], elevation [@moser_elevation_2011], and water availability [@newman_above-_2006]. That we do not see consistent patterns of variation in allocation across global climatic gradients indicates that the pressures influencing shifts in allocation between fluxes occur on local scales and/or in response to factors other than mean climate, including inter- and intra-annual climiatic fluctuations. ]

>>>>

[**NOBBY, please pay special attention to this paragraph**]. We show that FACF are broadly consistent in their responses to climate drivers on the global scale (with the exception of some differences in MAT-MAP interactions; Fig. 4), with no major trends in C allocation among the variable pairs tested (Fig. 2; **Some SI table**). Although variation in allocation has been observed along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]--along with non-climatic axes of stand age [@litton_carbon_2007], nutrient availability [@litton_carbon_2007; @gill_belowground_2016], and forest structure [@taylor_greater_2019]--variation in relation to climate is not apparent at the global scale within ForC, which contains the bulk of relevant data. Our conclusion, then, is that hypothesized gradients in allocation along global climate gradients cannot currently be supported for mature forests, although data quantity and standardization is currently insufficent to rule out the possibility that such trends exist. Of particular interest and significance are the relationships amongst $GPP$, net primary productivity ($NPP$ and its components, particularly $ANPP_{woody-stem}$), and respiration ($R_{auto}$, $R_{root}$). There have been suggestions that tropical forests tend to have low carbon use efficiency ($CUE$= $NPP$/$GPP$=($GPP$-$R_{auto}$/$GPP$), which are based on observations of low $CUE$ in old-growth tropical forests relative to extratropical forests [@de_lucia_forest_2007; Malhi 2012; @anderson-teixeira_carbon_2016], but our analysis suggests that these low values might more appropriately be attributed to the fact that these forests are old than to their tropical climate. Indeed, $CUE$ is known to decline with forest age ([@de_lucia_forest_2007];**REFS(NOBBY)**) but appears to be roughly independent of $GPP$ [@litton_carbon_2007]. Similarly, it has been suggested that maintenance costs ($R_{auto}$+ **XX** per unit biomass) increase more rapidly with temperature than does $GPP$ (Larjavaara & Muller-Landau 2011), implying that $ANPP_{woody-stem}$ would have a shallower slope than $GPP$. There is some indication that this may be the case (Fig. 2), but again careful methodological standardization across a consistent set of mature forest sites will be necessary to determine whether any global gradients in allocation exist.
